Lobbying and Legislative Uncertainty

### 2016-04-15 presentation.tex
add figures
finish intro and first half of model section

\section{Overview}
\subsection{Preview}
\begin{frame}{The Questions}

\pause
\begin{enumerate}[<+->]
\item When 
	\begin{itemize}
		\item E
	\end{itemize}
	\vskip.1in
\item Can
	\begin{itemize}
		\item G
	\end{itemize}
\end{enumerate}

@@

\begin{frame}{Some Data}

\pause
\begin{enumerate}[<+->]
\item When 
	\begin{itemize}
		\item E
	\end{itemize}
	\vskip.1in
\item Can
	\begin{itemize}
		\item G
	\end{itemize}
\end{enumerate}

@@

\begin{frame}{Preview}
\frametitle{P}
\pause
With . I:
\pause
\begin{itemize}[<+->]
	\item e
	\item c
		\begin{itemize}[<+->]
			\item b
			\item t
		\end{itemize}
	\item e
\end{itemize}
\end{frame}

\begin{frame}{Preview}
\frametitle{Results}

\pause
\begin{itemize}[<+->]
	\item S
	\item F
	\item D
		\begin{itemize}
			\item P
			\item M
		\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Literature}
\pause
\begin{itemize}[<+->]
	\item \textbf{Vote Buying in Legislatures}: 
	\item \textbf{Stochastic Voting}: 
	\item \textbf{Uncertainty}: 
\end{itemize}
\end{frame}

\pause
T
\pause
\begin{itemize}
	\item A
	\pause
	\item B
\end{itemize}

\begin{frame}{Timeline}
\pause
\begin{enumerate}[<+->]
	\item {\bfseries Who}
		\begin{enumerate}[i.]
			%\pause
			\item Governments 
		\end{enumerate}
	%\pause
	\item \textbf{Then}
		\begin{enumerate}[i.]
			%\pause
			\item A
			%\pause
			\item B
		\end{enumerate}
	%\pause
	\item \textbf{What}
	%\pause
		\begin{enumerate}[i.]
			\item If
		\end{enumerate}
\end{enumerate}
\end{frame}

>>>>

\section{Overview}
\subsection{Overview}
\begin{frame}{The Questions}

\pause
\begin{enumerate}[<+->]
\item How does uncertainty about legislators' preferences impact 
	\begin{itemize}
		\item lobbying strategies (e.g. who to lobby, how much to `pay')
		\item probability a bill passes
	\end{itemize}
	\vskip.1in
\item Can we distentangle fundamental uncertainty about preferences from equilibrium and modeling uncertainty?
	\begin{itemize}
		\item[$\Rightarrow$] Build a structural model to take to U.S. House data
	\end{itemize}
	\vskip.1in
\item Ultimately, want to identify cross-industry measures of legislative uncertainty
\end{enumerate}

@@

\begin{frame}{Some Stylized Facts}

\pause
\begin{enumerate}[<+->]
	\item In the U.S., about $\$ 4$ billion / yr spent on lobbying and campaign contributions
	\item There is usually lobbying on both sides of a given issue
	\item Moderate legislators receive more contributions than those that are ideologically extreme
	\item Legislators about whom there is a moderate level of uncertainty are lobbied the most
\end{enumerate}

\pause
\vskip.2in
Adding uncertainty to standard model captures (2) --- (4)
\end{frame}

\begin{frame}{Literature}
\pause
\begin{itemize}[<+->]
	\item \textbf{Vote Buying in Legislatures}: Groseclose $\&$ Snyder 1996, Banks 2000, Dal Bo 2007
	\item \textbf{Lobbying with Uncertainty}: Coates $\&$ Ludema 2001, Le Breton $\&$ Salanie 2003, Le Breton $\&$ Zaphorozhets (2007)
	\item \textbf{Probabilistic Voting with Policy Motivation}: Roemer 1994, 1997, Duggan $\&$ Fey 2011
	%\item \textbf{Uncertainty}: 
\end{itemize}
\end{frame}

%\begin{frame}
%\includegraphics[height=2.75in, width=4.25in]{graph2.jpg}
%\end{frame}

\begin{frame}
\includegraphics[height=2.75in, width=4.25in]{graph1.jpg}
\end{frame}

\begin{frame}{Preview}
\frametitle{Context}
\pause
U.S. House of Representative 
\pause
\begin{itemize}[<+->]
	\item All roll call votes, 2005 through present
	\item Interest group lobbying on each vote
	\item PAC contributions, LDA lobbying data
\end{itemize}

\vskip.2in
\pause
Use multi-dimensional ideal-point estimation to identify measures of uncertainty
\end{frame}

\begin{frame}
\includegraphics[height=2.75in, width=4.25in]{NSF_combined_graph.pdf}
\end{frame}

\pause
Three legislators
\pause
\begin{itemize}
	\item Identified by location in linear preference space: $i \in \left\{-0.5,0,.5\right\}$
	\item Each will vote for status quo $\bm{s}$ or new proposal $\bm{x}$
	\item Decision made by majority vote
\end{itemize}

\pause
\vskip.2in
Two vote buyers, $A$ and $B$
\pause
\begin{itemize}
	\item A prefers $x$, $B$ prefers $s$
\end{itemize}

@@

\begin{frame}{Timeline}
\pause
\begin{enumerate}[<+->]
	\item {\bfseries Vote Buyer A}
		\begin{enumerate}[i.]
			%\pause
			\item Chooses bribes $\un{a} = \left(a_{-.5},a_0,a_{.5}\right)$
		\end{enumerate}
	%\pause
	\item \textbf{Vote Buyer B}
		\begin{enumerate}[i.]
			%\pause
			\item Observes $\un{a}$
			%\pause
			\item Chooses bribes $\un{b} = \left(b_{-.5},b_0,b_{.5}\right)$
		\end{enumerate}
	%\pause
	\item \textbf{Legislature}
	%\pause
		\begin{enumerate}[i.]
			\item All legislators observe $\un{a},\un{b}$
			\item Uncertainty about preferences realized: $\un{\ta} = \left(\ta_{-.5},\ta_0,\ta_{.5}\right)$
			\item Each legislator votes for her preferred policy 
		\end{enumerate}
\end{enumerate}
\end{frame}
